Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-22 paper/v2/paper-edited.tex
reducing size
space reduction

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003068.10003073.10003075</concept_id>
<concept_desc>Networks~Network control algorithms</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003083.10003095</concept_id>
<concept_desc>Networks~Network reliability</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003099.10003104</concept_id>
<concept_desc>Networks~Network management</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011050.10011017</concept_id>
<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Networks~Network control algorithms}
\ccsdesc[300]{Networks~Network reliability}
\ccsdesc[300]{Networks~Network management}
\ccsdesc[300]{Software and its engineering~Automated static analysis}
\ccsdesc[300]{Software and its engineering~Domain specific languages}

\printccsdesc

\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
  \label{fig:unimplementable}
  %\vspace{-1em}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.67\columnwidth]{figures/loops}
  \caption{A Product Graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}
  \label{fig:avoiding-loops}
  %\vspace{-1em}
\end{figure}

@@

Consider the partial Product Graph shown in Figure~\ref{fig:avoiding-loops}. Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$. However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops. In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously. In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).

@@

\section*{Acknowledgments}

We thank R. Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595.

>>>>

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10003033.10003068.10003073.10003075</concept_id>
%<concept_desc>Networks~Network control algorithms</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10003033.10003083.10003095</concept_id>
%<concept_desc>Networks~Network reliability</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10003033.10003099.10003104</concept_id>
%<concept_desc>Networks~Network management</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
%<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10011006.10011050.10011017</concept_id>
%<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[300]{Networks~Network control algorithms}
%\ccsdesc[300]{Networks~Network reliability}
%\ccsdesc[300]{Networks~Network management}
%\ccsdesc[300]{Software and its engineering~Automated static analysis}
%\ccsdesc[300]{Software and its engineering~Domain specific languages}
%
%\printccsdesc
%
%\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}

\vspace{0.1in}
\noindent
\textbf{CCS Concepts}\\
$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;} 
$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}

\vspace{0.1in}
\noindent
\textbf{Keywords}\\
Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
  \label{fig:unimplementable}
  %\vspace{-1em}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.67\columnwidth]{figures/loops}
  \caption{A product graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}
  \label{fig:avoiding-loops}
  %\vspace{-1em}
\end{figure}

@@

Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}. Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$. However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops. In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously. In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).

@@

\para{Acknowledgements}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595.
